The Social Conditioning of Fear

### 2023-12-06 scripts/manuscript.qmd
recategorizing variables of interests

The third dimension we included were on :

>>>>

The third dimension we considered were individual-level health-related and  attitudinal variables. Good mental and physical health status is positively correlated with individuals' evaluation of their life conditions and affects how likely individuals are to report positive emotions about their life [@dwyer2017]. Additionally, social capital--such as levels of interpersonal trust and norms of reciprocity and mutual aid--is believed to play an important role in explaining variations in health status across geographic localities [@kawachi1999]. Therefore, we included the following variables that capture respondents' self-reported health status and assessment of interpersonal social climate:
